Calls vs IMD

### 2021-11-01 output/calls_vs_imd.Rmd
fixed IMD doc

# Load packages
library(fable)
library(lubridate)
library(tsibble)
library(tidyverse)
library(readxl)

@@

imd <- read_xlsx("C:\\Users\\maczo\\Desktop\\research\\n8_cov\\File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()

calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()

@@

@@

  type_df <- calls %>% filter(incident_type_new == inc_type)

  type_calls <- type_df %>% group_by(lsoa) %>% count() %>% 
    left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))

@@

@@

total_calls <- calls %>% group_by(lsoa) %>% count() %>% 
  left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))

>>>>

# Load packages
library(fable)
library(lubridate)
library(tsibble)
library(tidyverse)
library(readxl)
library(sf)

@@

# imd <- read_xlsx("C:\\Users\\maczo\\Desktop\\research\\n8_cov\\File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()

imd <- read_xlsx("/Users/reka/Dropbox (The University of Manchester)/N8_covid/analysis/n8_covid/File_1_-_IMD2019_Index_of_Multiple_Deprivation.xlsx", sheet = "IMD2019") %>%  janitor::clean_names()

cheshire_lsoas <- st_read("../cheshire_lsoas.geojson")
cheshire_imds <- left_join(cheshire_lsoas, imd, by = c("LSOA11NM" = "lsoa_name_2011"))

# calls <- read_csv("Z:\\n8_data_v2.csv.gz") %>%  janitor::clean_names()
calls <- read_csv("/Volumes/n8_covid/n8_data_v2.csv.gz") %>%  janitor::clean_names()

@@

cheshire_calls <- calls %>% filter(lsoa %in% unique(cheshire_imds$LSOA11NM))

@@

  type_calls <- cheshire_calls %>% filter(incident_type_new == inc_type) %>% 
    group_by(lsoa) %>% count() %>% 
    left_join(cheshire_imds, ., by = c("LSOA11NM" = "lsoa")) %>% 
    mutate(n = replace_na(n, 0))

@@

**NOTE** there are 17 LSOAs where the IMD ranking isn't there? It's not in the spreadsheet, IDK why so need to check. They are: `r cheshire_imds %>% filter(is.na(index_of_multiple_deprivation_imd_decile)) %>% pull(LSOA11NM)`

@@

total_calls <- cheshire_calls %>% group_by(lsoa) %>% count() %>% 
  left_join(., imd, by = c("lsoa" =  "lsoa_name_2011"))
